---
title: "Knapsack Vignette"
author: "Simge Cinar & Hugo Morvan"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Knapsack Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Loading the necessary library
```{r}
library(knapsack)
```

Generating the data
```{r}
RNGversion(min(as.character(getRversion()),"3.5.3"))
set.seed(42, kind = "Mersenne-Twister", normal.kind = "Inversion")
n <- 2000
knapsack_objects <-
  data.frame(
    w=sample(1:4000, size = n, replace = TRUE),
    v=runif(n = n, 0, 10000)
  )
```

## BRUTE FORCE SEARCH

This approach is of complexity O(2^n) since all possible combinations 2n needs to be evaluated. The run time for brute force search algorithm is 4.23 seconds with n = 16. (Time may vary depending on your computing power)

```{r}
x <- knapsack_objects[1:16,]
W <- 3500
```

```{r}
start_time <- Sys.time()
result <- brute_force_knapsack(x,W)
end_time <- Sys.time()
runtime <- end_time - start_time
cat("Runtime:", runtime, "seconds\n")
result
```

## DYNAMIC PROGRAMMING

This approach is of complexity O(Wn). The run time for dynamic programming is 36.50 seconds with n = 500. (Time may vary depending on your computing power)


```{r}
x <- knapsack_objects[1:500,]
W <- 3500
```

```{r}
start_time <- Sys.time()
result <- knapsack_dynamic(x, W)
end_time <- Sys.time()
runtime <- end_time - start_time
cat("Runtime without rcpp:", runtime, "seconds\n")
result
```
Using rcpp package, the code is executed faster and the run time decreased from 36.50 seconds to 5.92 seconds. (Time may vary depending on your computing power, but the improvement is proportional)

```{r}
start_time <- Sys.time()
result <- knapsack_dynamic(x, W, fast = TRUE)
end_time <- Sys.time()
runtime <- end_time - start_time
cat("Runtime with rcpp:", runtime, "seconds\n")
result
```

## GREEDY HEURISTIC

This approach is of complexity O(n log(n)). The run time for greedy heuristics is 0.35 seconds with n = 1,000,000 (Time may vary depending on your computing power). This algorithm is really fast but it does not guarantee to find the best solution unlike dynamic programming and brute force search algorithm

```{r}
m <- 1000000
knapsack_million_objects <-
  data.frame(
    w=sample(1:4000, size = m, replace = TRUE),
    v=runif(n = m, 0, 10000)
  )
x <- knapsack_million_objects[1:1000000,]
W <- 3500
```

```{r}
start_time <- Sys.time()
result <- greedy_knapsack(x,W)
end_time <- Sys.time()
runtime <- end_time - start_time
cat("Runtime:", runtime, "seconds\n")
result
```




